The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-12-31 paper.tex
Added a referee response file.

\sihui{
\subsection{Repeater networks}
}

\section{Optical switching}

>>>>

\sihui{
\subsection{Repeater networks}

Quantum repeaters are devices that distribute entanglement across a network, or teleport quantum states between nodes of a network. The purpose of such a quantum network is to communicate and process quantum information over long distances. While photons serve as great medium for information transfer, many implementations of photonic repeater network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98}, quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}. The seminal work of Duan et al.~ \cite{Duan01}, in particular, uses atomic ensemble as quantum memories. Single photon interference then facilitates creation of entanglement between them. However, this makes the repeater node susceptible to interferometric instability which later schemes improve upon by using two-photon interference instead \cite{Zhao07,YCZCS08,CZCS07}. Error correction codes for photon loss and dark counts \cite{bib:RHG05} have also been applied for use in repeaters \cite{bib:MHSDN10,bib:Muralidhara14,bib:Ewert16,bib:Ewert17}. Another scheme combines the use of two-photon interference and spectral multiplexing to boost high entanglement distribution rates \cite{bib:Sinclair14}.

Without the use of repeaters, it has been shown that the rate transmission of a channel with loss without entanglement assistance has a linear fallout \cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound. The minimal resources required to exceed the TGW bound is a subject of active research, and so far it has been shown that the performance of the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al. \cite{bib:Sinclair14} are able to exceed the TGW bound. Other benchmarking tools have also been used to analyze many of these repeater schemes in detail \cite{bib:Muralidhara16}. More details about repeaters and long-distance quantum communication can be found in review papers on these subjects \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}.

}
\section{Optical switching}
